Privacy Calculus Experiment

### 2020-06-16 index.Rmd
- changed title

On this website, you can find the companion material for the paper _How Do Like and Dislike Buttons Affect Communication? A Privacy Calculus Approach to Understanding Self-Disclosure Online in a One-Week Field Experiment_.

You can either read the paper [online](manuscript.html) or download it as [pdf](manuscript.pdf). You can also find the detailed code and summaries of the [analyses](analyses.html) that were reported in the paper, as well as [additional analyses](analyses_additional.html) not reported in the paper.

>>>>

On this website, you can find the companion material for the paper _How Do Like and Dislike Buttons Affect Communication? Testing the Privacy Calculus in a Preregistered One-Week Field Experiment_.

You can either read the paper [in your browser](manuscript.html) or download it as [pdf](manuscript.pdf). You can also find the detailed code and summaries of the [analyses](analyses.html) reported in the paper, as well as [additional analyses](analyses_additional.html) not reported in the paper.

### 2020-06-16 manuscript.RmD
- changed title

---
title             : "How Do Like and Dislike Buttons Affect Communication? A Privacy Calculus Approach to Understanding Self-Disclosure Online in a One-Week Field Experiment"
shorttitle        : "Popularity cues and the privacy calculus"
author:            
  - name          : "Dienlin, Tobias"
    email         : "tobias.dienlin@uni-hohenheim.de"
    affiliation   : "1"
    corresponding : yes
    address       : "University of Hohenheim, Department of Media Psychology (540F), 70599 Stuttgart, Germany"
  - name          : "Braeunlich, Katharina"
    email         : "braeunlich@uni-koblenz.de"
    affiliation   : "2"
  - name          : "Trepte, Sabine"
    email         : "sabine.trepte@uni-hohenheim.de"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "University of Hohenheim"
  - id            : "2"
    institution   : "University of Koblenz-Landau"
author_note: |
    All authors contributed extensively to the work presented in this paper. TD, KB, & ST designed the study; KB & TD designed the online website; TD & KB administered the data collection and importation; TD wrote the code, ran the models, and analyzed the output data; TD wrote the manuscript and ST provided comments; ST supervised the project.

@@

    This manuscript features a companion website, which includes the data, code, additional analyses, and a reproducible version of the manuscript (https://tdienlin.github.io/privacy_calc_exp).
abstract: |
    According to the privacy calculus, both privacy concerns and expected gratifications explain self-disclosure online. So far, however, most findings were based on self-reports, and little is known about whether the privacy calculus can be used to explain observations of actual behavior. Likewise, we still know little as to whether the privacy calculus is influenced by the design of online websites, including for example popularity cues such as like and dislike buttons. To answer these questions, we ran a preregistered one-week field experiment. Participants were randomly distributed to three different websites, on which they discussed a current political topic. The websites featured either (a) like buttons, (b) like and dislike button, or (c) no like/dislike buttons, and were otherwise identical. The final sample consisted of `r knitr::load_cache(label = "load-data", object = "n_matched")` participants. Although the originally preregistered model was rejected, the results showed that a considerable share of actual self-disclosure could be explained by privacy concerns, gratifications, privacy deliberation, trust, and self-efficacy. The impact of the popularity cues on self-disclosure and the privacy calculus was negligible.
keywords          : "privacy calculus, self-disclosure, popularity cues, field experiment, structural equation modeling, preregistration"
bibliography      : 
  - [bibliography/r-references.bib]
  - [bibliography/references.bib]
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
draft             : no
documentclass     : "apa6"
classoption       : "man"
# to compile as pdf
# (a) move file "_site.yml" to folder "tmp"
# (b) uncomment the following lines
# output            : papaja::apa6_pdf
# header-includes:
#   - \setlength{\parskip}{0em}
#   - \raggedbottom
#   - \note{\clearpage}
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
---

@@

<!-- # Introduction -->

@@

However, although the privacy calculus has gained momentum in academic research, several important questions remain unanswered. 
First, we still know little about whether the privacy calculus can be replicated with behavioral data in an authentic long-term setting [@kokolakisPrivacyAttitudesPrivacy2017]. 
Thus far, most research supporting the privacy calculus has used either self-reports of behavior [e.g., @krasnovaOnlineSocialNetworks2010], vignette approaches [e.g., @bolUnderstandingEffectsPersonalization2018], or one-shot experiments in the lab [e.g., @treptePrivacyCalculusContextualized2020]. 
Still missing is a long-term field study in which actual behavior is observed in an authentic context.

@@

As mentioned above, there is still a shortage of studies explicitly analyzing the decision process behind the disclosing of information---although this point of criticism has been leveled several times [@knijnenburgDeathPrivacyCalculus2017] and although other fields such as behavioral economics have long focused on the underlying problem [@zhuPrivacyCalculusIts2017]. 
This criticism is justified.
The observation that privacy concerns and expected gratifications are related to self-disclosure is by itself not sufficient evidence for an explicit weighing process.
Hence, research on the privacy calculus would benefit significantly from analyzing this decision process explicitly. 
Building on @omarzuDisclosureDecisionModel2000 and @altmanPrivacyConceptualAnalysis1976, we hence address a novel concept that might best be termed _privacy deliberation_, which captures the extent to which individual people explicitly compare potential positive and negative outcomes before communicating with others.

@@

Several attempts have already been made to expand the privacy calculus, introducing additional variables such as self-efficacy or trust [@dinevExtendedPrivacyCalculus2006]. 
Self-efficacy in the context of the privacy calculus captures whether people believe in their own capability to implement particular privacy behaviors in the future [@dienlinExtendedPrivacyCalculus2016].
These privacy behaviors refer to either self-_disclosure_ (e.g., publishing a blog post) or self-_withdrawal_ (e.g., deleting inappropriate content).
People who report more privacy self-efficacy also engage in more self-withdrawal  [@chenRevisitingPrivacyParadox2018].
In light of our focus on active communication, in this study we investigate the influence of self-_disclosure_ self-efficacy.

@@

The next variable, trust, can be conceptualized in two different ways [@gefenTrustTAMOnline2003]: 
It either captures "_specific_ beliefs dealing primarily with the integrity, benevolence, and ability of another party" [@gefenTrustTAMOnline2003, p. 55, emphasis added] or a "_general_ belief that another party can be trusted" [@gefenTrustTAMOnline2003, p.55, emphasis added]. 
Whereas specific trust focuses on the causes of trust, general trust emphasized the experience of trust.
@gefenTrustTAMOnline2003 prioritize specific trust (p. 60). 
In the online context, it is also important to differentiate among several _targets_ of trust [@sollnerWhyDifferentTrust2016]. 
Potential targets include (a) the information system, (b) the provider, (c) the Internet, and (d) the community of other users [@sollnerWhyDifferentTrust2016]. 
Trust plays a key role in online communication [@metzgerPrivacyTrustDisclosure2004]. 
For example, people who put more trust in the providers of networks also disclose more personal information [@liEmpiricalStudiesOnline2011].

@@

In this vein, it seems plausible that popularity cues might also impact the privacy calculus [@kramerMasteringChallengeBalancing2020], and that they serve as a means of reward and punishment. 
Receiving a like online is similar to receiving a compliment offline. 
Likes are positive and represent the positivity bias typical of social media [@reineckeAuthenticityWellbeingSocial2014]. 
Introducing the option to receive likes thereby affords and emphasizes a _gain frame_
(see also @rosoffHeuristicsBiasesCyber2013). 
These gains can be garnered only through participation. 
In addition, because positive outcomes are emphasized, it is likely that concerns decrease. 
Finally, in situations where there is more to win, one needs to deliberate whether one wants to partake.
Implementing like buttons might therefore also make people more actively deliberate about whether or not to disclose information.

@@

We ran a priori power analyses to determine how many participants to recruit. The power analysis was based on a smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018]. 
In other words, we defined a minimum effect size that we would consider sufficiently large enough to support our hypotheses. 
Because small effects should be expected when researching aspects of privacy online [e.g., @baruhOnlinePrivacyConcerns2017], with small effects beginning at an effect size of _r_ = .10 [@cohenPowerPrimer1992], we set our SESOI to be _r_ = `r r_sesoi %>% my_round("std")`. 
Our aim was to be able to detect this SESOI with a probability of at least 95%. Using the regular alpha level of 5%, basic power analyses revealed a minimum sample size of _n_ = `r n_desired %>% format(big.mark = ",")`. 
In the end, we were able to include n = `r n_final` in our analyses (see below). 
This means that our study had a probability (power) of `r power_achieved * 100`% to find an effect at least as large as _r_ = `r r_sesoi %>% my_round("std")`. 
Put differently, we were able to make reliable inferences (i.e., power = 95%) about effects at least as big as _r_ = `r r_sensitive %>% my_round("std")`.

We collected a representative sample of the German population in terms of age, sex, and federal state. 
`r n_t1 %>% format(big.mark = ",")` participants completed the survey at T1, `r n_users` participants created a user account on the website,  and `r n_t2` participants completed the survey at T2. 
Using tokens and IP addresses, we connected the data from T1, participants' behavior on the website, and T2 by means of objective and automated processes.
Unfortunately, the data of several participants could not be matched for technical reasons, for example because they used different devices for the respective steps.
In the end, the data of _n_ = `r n_matched` participants could be matched successfully.
We excluded _n_ = `r n_speeding` participants who finished the questionnaire at T2 in less than three minutes, which we considered to be unreasonably fast.[^note] 
To detect potentially corrupt data, we calculated Cook's distance.
We excluded `r english::english(n_resp_pattern)` participants who provided clear response patterns (i.e., straight-lining). 
The final sample included `r n_final` participants.
The sample characteristics at T1 and T2 were as follows: 
T1: Age = `r round(age_t1_m, 0)` years, sex = `r round(male_t1_m, 2)*100`% male, college degree = `r round(college_t1_m, 2)*100`%.
T2: Age = `r round(age_final_m, 0)` years, sex = `r round(male_final_m, 2)*100`% male, college degree = `r round(college_final_m * 100, 0)`%.
One participant did not report his or her sex.

@@

In what follows, we present the materials we used to measure our variables. 
Wherever possible, we operationalized the variables using established measures.
Where impossible (for example, to date there exists no scale on privacy deliberation), we self-designed novel items, which we pretested concerning legibility and understandability.
To assess factor validity we ran confirmatory factor analyses (CFA). 
If the CFAs revealed insufficient fit, we deleted malfunctioning items. 
All items were formulated as statements to which participants indicated their (dis-)agreement on a bipolar 7-point scale. 
Answer options were visualized as follows: -3 (_strongly disagree_), -2 (_disagree_), -1 (_slightly disagree_), 0 (_neutral_), +1 (_slightly agree_), +2 (_agree_), +3 (_strongly agree_). 
For the analyses, answers were coded from 1 to 7.
In the questionnaire, all items measuring a variable were presented on the same page in randomized order.

@@

Privacy concerns were measured with seven items based on @buchananDevelopmentMeasuresOnline2007.
One example item was "When using the participation platform, I had concerns about my privacy". 
One item had to be deleted due to poor psychometric properties.

@@

We differentiated between two separate types of gratification. 
_General gratifications_ were measured with five items based on @sunLocationInformationDisclosure2015.
One example item was "Using the participation platform has paid off for me". 
_Specific gratifications_ were measured with 15 items on five different subdimensions with three items each. 
The scaled was based on @schererGratifikationMinuteZeitnahe2002.
Example items were: "Using the participation platform made it possible for me to" ... "learn things I would not have noticed otherwise" (information), "react to a subject that is important to me" (relevance), "engage politically" (political participation), "try to improve society" (idealism), and "soothe my guilty consciences" (extrinsic benefits).

@@

Self-disclosure was calculated by taking the log scale of the number of words each participant wrote in a comment, to which we added the number of likes and dislikes, which were multiplied by two. 
The number of likes and dislikes were multiplied by two because, rudimentarily, like buttons abbreviate the sentence “I like” and dislike buttons “I dislike”.
The sum of words and likes/dislikes was log-scaled because the relative amount of self-disclosure diminishes the more a person has already expressed.

@@

We first measured and plotted all bivariate relations between the study variables (see Figure \@ref(fig:corrplot)). 
The results did not reveal any relationships to be particularly curvilinear. 
Furthermore, all variables referring to the privacy calculus demonstrated the expected relationships with self-disclosure. 
For example, people who were more concerned about their privacy disclosed less information (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "pri_con" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")`). 
Worth noting, specific gratifications and general trust predicted self-disclosure better than general gratifications and specific trust (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_gen" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")` vs. _r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_spec" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")`).
The mean of privacy deliberation was _m_ = `r des_pridel$m %>% round(2)`. Altogether, `r pridel_active %>% round(0)`% of participants reported having actively deliberated about their privacy.

@@

When comparing the three models with one another, the adapted model explained the most variance in self-disclosure (`r rsquare_fit_adapted * 100` %), followed by the preregistered model (`r rsquare_fit_prereg * 100` %), and the simple privacy calculus model (`r rsquare_fit_simple * 100` %).
At the same time, the simple privacy calculus model was the most parsimonious one (BIC = `r model_comp_tab["simple", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["simple", "aic"] %>% round(0) %>% format(big.mark = ",")`), followed by the preregistered model (BIC = `r model_comp_tab["preregistered", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["preregistered", "aic"] %>% round(0) %>% format(big.mark = ",")`), and the adapted model (BIC = `r model_comp_tab["adapted", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["adapted", "aic"] %>% round(0) %>%  format(big.mark = ",")`).
For a visual overview of all results, see Figure \@ref(fig:plotpc).

@@

The adapted model suggests that also when holding all other variables constant, people who deliberate more about their privacy disclose less, and that people who expect more specific gratifications and who feel more self-efficacious disclose more.
However, the model also suggests that if trust increases, while all other factors remain constant, self-disclosure decreases.
This is theoretically implausible. 
As a result, we also fit the above-mentioned simple privacy calculus model, which showed that both privacy concerns and obtained gratifications significantly and meaningfully predicted self-disclosure. 
Taken together, the results support the privacy calculus framework and suggest that self-disclosure online is not erratic and that it can be explained by several psychological variables.

Aligned with this observation, the results also suggest that in new communication contexts at least one third of all Internet users _actively deliberates_ about their privacy. 
Determining whether this figure is large or small is a normative question.
Although the effect seems substantial, one could argue that it should be higher and that more people in our society should actively deliberate about their self-disclosure practices online. 
Interestingly, results showed that privacy deliberation and privacy concerns were remarkably similar, which was evidenced by their strong correlation with one another and their comparable correlations with other variables. 
This either implies that thinking about one's privacy increases one's concern or, conversely, that being concerned about one's privacy leads one to think about one's options more actively. 
Future research might tell.

The next major implication is that popularity cues do not always seem to have a strong influence on the privacy calculus and self-disclosure.
Although some studies have found that popularity cues can substantially impact behavior [e.g., @muchnikSocialInfluenceBias2013], in our study we found the opposite.
Users still disclosed the same amount of personal information regardless of whether or not a website included like or dislike buttons, potentially highlighting the agency of users.
This is of course not to say that popularity cues have no impact on the privacy calculus in general. 
Instead, the results only suggest that there exist certain situations and instances in which the influence of popularity cues is negligible.

@@

From a _theoretical_ perspective, multicollinearity could also suggest that the underlying theoretical model is ill-configured.
It is our understanding that multiple regression is often used with the aim to isolate effects, to make sure that they are not simply caused by another third variable.
However, in cases of highly correlated measures this often does not make much sense theoretically.
For example, in our case combining trust and gratification asks how increasing benefits affects self-disclosure _while holding trust constant_.
Theoretically, however, it is more plausible to assume that increasing gratifications also fosters trust [@sollnerWhyDifferentTrust2016].
In the preregistered analysis we even went further and tested whether trust increases self-disclose while holding constant gratifications, privacy concerns, privacy deliberations, and self-efficacy, measures which are all strongly correlated. 
In short, the effects we found could even be correct, but the interpretation is much more difficult, artificial, and thereby of little theoretical and practical value.

>>>>

---
title             : "How Do Like and Dislike Buttons Affect Communication? Testing the Privacy Calculus in a Preregistered One-Week Field Experiment"
shorttitle        : "Popularity cues and the privacy calculus"
author:            
  - name          : "Dienlin, Tobias"
    email         : "tobias.dienlin@uni-hohenheim.de"
    affiliation   : "1"
    corresponding : yes
    address       : "University of Hohenheim, Department of Media Psychology (540F), 70599 Stuttgart, Germany"
  - name          : "Braeunlich, Katharina"
    email         : "braeunlich@uni-koblenz.de"
    affiliation   : "2"
  - name          : "Trepte, Sabine"
    email         : "sabine.trepte@uni-hohenheim.de"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "University of Hohenheim"
  - id            : "2"
    institution   : "University of Koblenz-Landau"
author_note: |
    All authors contributed extensively to the work presented in this paper. TD, KB, & ST designed the study; KB & TD designed the online website; TD & KB administered the data collection and importation; TD wrote the code, ran the models, and analyzed the output data; TD wrote the manuscript and ST provided comments; ST supervised the project.

@@

    This manuscript features a companion website, which includes the data, code, additional analyses, the preregistration, and a reproducible version of the manuscript (https://tdienlin.github.io/privacy_calc_exp).
abstract: |
    According to the privacy calculus, both privacy concerns and expected gratifications explain self-disclosure online. So far, however, most findings were based on self-reports, and little is known about whether the privacy calculus can be used to explain observations of actual behavior. Likewise, we still know little as to whether the privacy calculus is influenced by the design of online websites, including for example popularity cues such as like and dislike buttons. To answer these questions, we ran a preregistered one-week field experiment. Participants were randomly distributed to three different websites, on which they discussed a current political topic. The websites featured either (a) like buttons, (b) like and dislike button, or (c) no like/dislike buttons, and were otherwise identical. The final sample consisted of `r knitr::load_cache(label = "load-data", object = "n_matched")` participants. Although the originally preregistered model was rejected, the results showed that a considerable share of actual self-disclosure could be explained by privacy concerns, gratifications, privacy deliberation, trust, and self-efficacy. The impact of the popularity cues on self-disclosure and the privacy calculus was negligible.
keywords          : "privacy calculus, self-disclosure, popularity cues, field experiment, structural equation modeling, preregistration"
bibliography      : 
  - [bibliography/r-references.bib]
  - [bibliography/references.bib]
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
draft             : no
documentclass     : "apa6"
classoption       : "man"
# to compile as pdf
# (a) move file "_site.yml" to folder "tmp"
# (b) uncomment the following lines
# output            : papaja::apa6_pdf
# header-includes:
#   - \setlength{\parskip}{0em}
#   - \raggedbottom
#   - \note{\clearpage}
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
---

@@

# Introduction

@@

However, although the privacy calculus has gained momentum in academic research, several important questions remain unanswered. 
First, we still know little about whether the privacy calculus can be replicated with behavioral data in an authentic long-term setting [@kokolakisPrivacyAttitudesPrivacy2017]. 
Thus far, most research supporting the privacy calculus has used either self-reports of behavior [e.g., @krasnovaOnlineSocialNetworks2010], vignette approaches [e.g., @bolUnderstandingEffectsPersonalization2018], or one-shot experiments in the lab [e.g., @treptePrivacyCalculusContextualized2020]. 
Still missing is a more long-term field study in which actual behavior is observed in an authentic context.

@@

As mentioned above, there is still a shortage of studies explicitly analyzing the decision process behind the disclosing of information---although this point of criticism has been leveled several times [@knijnenburgDeathPrivacyCalculus2017] and although other fields such as behavioral economics have long focused on the underlying problem [@zhuPrivacyCalculusIts2017]. 
This criticism is justified.
The observation that privacy concerns and expected gratifications are related to self-disclosure is by itself not sufficient evidence for an explicit weighing process.
Hence, research on the privacy calculus would benefit from analyzing this decision process explicitly. 
Building on @omarzuDisclosureDecisionModel2000 and @altmanPrivacyConceptualAnalysis1976, we hence address a novel concept that might best be termed _privacy deliberation_, which captures the extent to which individual people explicitly compare potential positive and negative outcomes before communicating with others.

@@

Several attempts have already been made to expand the privacy calculus, introducing additional variables such as self-efficacy or trust [@dinevExtendedPrivacyCalculus2006]. 
Self-efficacy in the context of the privacy calculus captures whether people believe in their own capacity to implement particular privacy behaviors in the future [@dienlinExtendedPrivacyCalculus2016].
These privacy behaviors refer to either _self-disclosure_ (e.g., publishing a blog post) or _self-withdrawal_ (e.g., deleting inappropriate content).
People who report more privacy self-efficacy also engage in more self-withdrawal  [@chenRevisitingPrivacyParadox2018].
In light of our focus on active communication, in this study we investigate the influence of _self-disclosure_ self-efficacy.

@@

The next variable, trust, can be conceptualized in two different ways [@gefenTrustTAMOnline2003]: 
It either captures "_specific_ beliefs dealing primarily with the integrity, benevolence, and ability of another party" [@gefenTrustTAMOnline2003, p. 55, emphasis added] or a "_general_ belief that another party can be trusted" [@gefenTrustTAMOnline2003, p.55, emphasis added]. 
Whereas specific trust focuses on the causes of trust, general trust emphasizes the experience of trust.
@gefenTrustTAMOnline2003 prioritize specific trust (p. 60). 
In the online context, it is also important to differentiate among several _targets_ of trust [@sollnerWhyDifferentTrust2016]. 
Potential targets include (a) the information system, (b) the provider, (c) the Internet, and (d) the community of other users [@sollnerWhyDifferentTrust2016]. 
Trust plays a key role in online communication [@metzgerPrivacyTrustDisclosure2004]. 
For example, people who put more trust in the providers of networks also disclose more personal information [@liEmpiricalStudiesOnline2011].

@@

In this vein, it seems plausible that popularity cues might also impact the privacy calculus [@kramerMasteringChallengeBalancing2020], and that they serve as a means of reward and punishment. 
Receiving a like online is similar to receiving a compliment offline. 
Likes are positive and represent the positivity bias typical of social media [@reineckeAuthenticityWellbeingSocial2014]. 
Introducing the option to receive likes mighty thereby afford and emphasize a _gain frame_
(see also @rosoffHeuristicsBiasesCyber2013). 
These gains can be garnered only through participation. 
In addition, because like buttons emphasize positive outcomes, it is likely that concerns decrease. 
Finally, in situations where there is more to win, people should more actively deliberate about whether or not to disclose information.

@@

We ran a priori power analyses to determine how many participants to recruit. The power analysis was based on a smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018]. 
In other words, we defined a minimum effect size that we considered sufficiently large enough to support our hypotheses. 
Because small effects should be expected when researching aspects of privacy online [e.g., @baruhOnlinePrivacyConcerns2017], with standardized small effects beginning at an effect size of _r_ = .10 [@cohenPowerPrimer1992], we set our SESOI to be _r_ = `r r_sesoi %>% my_round("std")`. 
Our aim was to be able to detect this SESOI with a probability of at least 95%. Using the regular alpha level of 5%, basic power analyses revealed a minimum sample size of _n_ = `r n_desired %>% format(big.mark = ",")`. 
In the end, we were able to include n = `r n_final` in our analyses (see below). 
This means that our study had a probability (power) of `r power_achieved * 100`% to find an effect at least as large as _r_ = `r r_sesoi %>% my_round("std")`. 
Put differently, we were able to make reliable inferences (i.e., power = 95%) about effects at least as big as _r_ = `r r_sensitive %>% my_round("std")`.

We collected a representative sample of the German population in terms of age, sex, and federal state. 
`r n_t1 %>% format(big.mark = ",")` participants completed the survey at T1, `r n_users` participants created a user account on the website,  and `r n_t2` participants completed the survey at T2. 
Using tokens and IP addresses, we connected the data from T1, participants' behavior on the website, and T2 by means of objective and automated processes.
The data of several participants could not be matched for technical reasons, for example because they used different devices for the respective steps.
In the end, the data of _n_ = `r n_matched` participants could be matched successfully.
We excluded _n_ = `r n_speeding` participants who finished the questionnaire at T2 in less than three minutes, which we considered to be unreasonably fast.[^note] 
To detect potentially problematic data, we calculated Cook's distance.
We excluded `r english::english(n_resp_pattern)` participants who provided clear response patterns (i.e., straight-lining). 
The final sample included `r n_final` participants.
The sample characteristics at T1 and T2 were as follows: 
T1: Age = `r round(age_t1_m, 0)` years, sex = `r round(male_t1_m, 2)*100`% male, college degree = `r round(college_t1_m, 2)*100`%.
T2: Age = `r round(age_final_m, 0)` years, sex = `r round(male_final_m, 2)*100`% male, college degree = `r round(college_final_m * 100, 0)`%.
One participant did not report his or her sex.

@@

In what follows, we present the materials we used to measure the variables. 
Wherever possible, we operationalized the variables using established measures.
Where impossible (for example, to date there exists no scale on privacy deliberation), we self-designed novel items, which we pretested concerning legibility and understandability.
To assess factor validity we ran confirmatory factor analyses (CFA). 
If the CFAs revealed insufficient fit, we deleted malfunctioning items. 
All items were formulated as statements to which participants indicated their (dis-)agreement on a bipolar 7-point scale. 
Answer options were visualized as follows: -3 (_strongly disagree_), -2 (_disagree_), -1 (_slightly disagree_), 0 (_neutral_), +1 (_slightly agree_), +2 (_agree_), +3 (_strongly agree_). 
For the analyses, answers were coded from 1 to 7.
In the questionnaire, all items measuring a variable were presented on the same page in randomized order.

@@

Privacy concerns were measured with seven items based on @buchananDevelopmentMeasuresOnline2007.
One example item was "When using the participation platform, I had concerns about my privacy". 
One item was deleted due to poor psychometric properties.

@@

We differentiated between two separate types of gratifications. 
_General gratifications_ were measured with five items based on @sunLocationInformationDisclosure2015.
One example item was "Using the participation platform has paid off for me". 
_Specific gratifications_ were measured with 15 items on five different subdimensions with three items each. 
The scaled was based on @schererGratifikationMinuteZeitnahe2002.
Example items were: "Using the participation platform made it possible for me to" ... "learn things I would not have noticed otherwise" (information), "react to a subject that is important to me" (relevance), "engage politically" (political participation), "try to improve society" (idealism), and "soothe my guilty consciences" (extrinsic benefits).

@@

Self-disclosure was calculated by taking the log scale of the number of words each participant wrote in a comment, to which we added the number of likes and dislikes, which were multiplied by two (preregistered). 
The number of likes and dislikes were multiplied by two because, rudimentarily, like buttons abbreviate the sentence “I like” and dislike buttons “I dislike”.
The sum of words and likes/dislikes was log-scaled because the relative amount of self-disclosure diminishes the more a person has already expressed.

@@

We first measured and plotted all bivariate relations between the study variables (see Figure \@ref(fig:corrplot)). 
The results did not reveal any relationships to be particularly curvilinear. 
Furthermore, all variables referring to the privacy calculus demonstrated the expected relationships with self-disclosure. 
For example, people who were more concerned about their privacy disclosed less information (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "pri_con" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")`). 
Worth noting, specific gratifications predicted self-disclosure better than general gratifications (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_spec" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")` vs. _r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_gen" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")`).
The mean of privacy deliberation was _m_ = `r des_pridel$m %>% round(2)`. Altogether, `r pridel_active %>% round(0)`% of participants reported having actively deliberated about their privacy.

@@

When comparing the three models with one another, the adapted model explained the most variance in self-disclosure (`r round(rsquare_fit_adapted * 100, 2)` %), followed by the preregistered model (`r round(rsquare_fit_prereg * 100, 2)` %), and the simple privacy calculus model (`r round(rsquare_fit_simple * 100, 2)` %).
At the same time, the simple privacy calculus model was the most parsimonious one (BIC = `r model_comp_tab["simple", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["simple", "aic"] %>% round(0) %>% format(big.mark = ",")`), followed by the preregistered model (BIC = `r model_comp_tab["preregistered", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["preregistered", "aic"] %>% round(0) %>% format(big.mark = ",")`), and the adapted model (BIC = `r model_comp_tab["adapted", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["adapted", "aic"] %>% round(0) %>%  format(big.mark = ",")`).
For a visual overview of all results, see Figure \@ref(fig:plotpc).

@@

The adapted model suggests that also when holding all other variables constant, people who deliberate more about their privacy disclose less, and that people who expect more specific gratifications and who feel more self-efficacious disclose more.
However, the model also suggests that if trust increases, while all other factors remain constant, self-disclosure decreases.
This seems theoretically implausible. 
As a result, we also fit the above-mentioned simple privacy calculus model, which showed that both privacy concerns and obtained gratifications significantly and meaningfully predicted self-disclosure. 
Taken together, the results support the privacy calculus framework and suggest that---at least in specific contexts---self-disclosure online is not erratic and that it can be explained by several psychological variables.

Aligned with this observation, the results also suggest that in new communication contexts at least one third of all Internet users _actively deliberates_ about their privacy. 
Determining whether this figure is large or small is a normative question.
Although the effect seems substantial to us, one could argue that it should be higher and that more people should actively deliberate about their self-disclosure practices online. 
Interestingly, results showed that privacy deliberation and privacy concerns were remarkably similar, which was evidenced by their strong correlation with one another and their comparable correlations with other variables. 
This either implies that thinking about one's privacy increases one's concern or, conversely, that being concerned about one's privacy leads one to think about one's options more actively. 
Future research might tell.

The next major implication is that popularity cues do not always seem to have a strong influence on the privacy calculus and self-disclosure.
Although some studies have found that popularity cues can substantially impact behavior [e.g., @muchnikSocialInfluenceBias2013], in our study we found the opposite.
Users still disclosed the same amount of personal information regardless of whether or not a website included like or dislike buttons, potentially highlighting the agency of users.
This is of course not to say that popularity cues have no impact on the privacy calculus in general. 
Instead, the results only suggest that there exist certain contexts in which the influence of popularity cues is negligible.

@@

From a _theoretical_ perspective, multicollinearity could also suggest that the underlying theoretical model is ill-configured.
It is our understanding that multiple regression is often used with the aim to isolate effects, to make sure that they are not simply caused by another third variable.
However, in cases of highly correlated measures this often does not make much sense theoretically.
For example, in our case combining trust and gratification asks how increasing benefits affects self-disclosure _while holding trust constant_.
Theoretically, however, it is more plausible to assume that increasing gratifications also automatically increases trust [@sollnerWhyDifferentTrust2016].
In the preregistered analysis we even went further and tested whether trust increases self-disclose while holding constant gratifications, privacy concerns, privacy deliberations, and self-efficacy---measures which are all strongly correlated. 
In short, the effects we found could even be correct, but the interpretation is more difficult, potentially artificial, and thereby of little theoretical and practical value.
